---
title: "analyse_laktat_seasons"
author: "ari"
date: "1 6 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lubridate)

library(readxl)

library(patchwork)
library(GGally)

source("functions/aggregate_seasons.R")
```

get the laktat data:
- dates and calculated values
- aggregate history of the 8 weeks before


### read Laktat test data
```{r}

path_laktat <- "C:/Users/rigle/Documents/Training/Laktat FTP/"

lactat_calculated  <-read_csv2(str_c(path_laktat,"laktat_watt.csv")) %>% rename("date" = "datum")


hour_of_power = tibble(date = as.Date(c("2017-05-22", "2017-03-24", "2016-07-20")),
                       w_5mmol = c(286, 282, 261))


lactat_calculated <- lactat_calculated  %>%  
                                            bind_rows(hour_of_power) %>% 
                          distinct(date, .keep_all = TRUE)


```



### Read export data from Goldencheetah

```{r}
data_gc <- read_gc_data("Results/goldencheetah_tss.csv")
```

```{r}
data_gc %>% group_by(year(date)) %>% count() 
```





```{r}
data_gc %>% ggplot(aes(x=date))+
  geom_point(aes(y = hr_watt) )+
  geom_smooth((aes(y=hr_watt)))+
  coord_cartesian(ylim = c(0,2))
```

```{r}
data_gc %>% ggplot(aes(x=date))+
  geom_point(aes(y = duration) )+
  geom_smooth((aes(y=duration)))
```

```{r}
data_gc %>% mutate(week = week(date),
                   year = year(date)) %>%
  group_by(year,week) %>% 
  summarise(TSS =sum(TSS,na.rm = TRUE),
            date =min(date)) %>%
ggplot(aes(x=date))+
  geom_point(aes(y = TSS) )+
  geom_smooth((aes(y=TSS)))+
  labs(y = "TSS/ week")+
  theme_light()
```

```{r}
data_gc %>% mutate(week = week(date),
                   year = year(date)) %>%
  group_by(year,week) %>% 
  summarise(duration =sum(duration,na.rm = TRUE),
            TSS =sum(TSS,na.rm = TRUE),
            date =min(date)) %>%
  mutate(TSS_duration = TSS/duration) %>%
ggplot(aes(x=date))+
  geom_point(aes(y = TSS_duration) )+
  geom_smooth((aes(y=TSS_duration)))+
  labs(y = "TSS/ duration / week")+
  theme_light()
```

```{r}
data_gc %>% mutate(week = week(date),
                   year = year(date)) %>%
  group_by(year,week) %>% 
  summarise(watt =mean(w_mean,na.rm = TRUE),
            hr =mean(hr,na.rm = TRUE),
            date =min(date)) %>%
  mutate(hr_watt = hr/watt) %>%
  
  filter(hr_watt < 1.5) %>%
  
ggplot(aes(x=date))+
  geom_point(aes(y = hr_watt) )+
  geom_smooth((aes(y=hr_watt)))+
  geom_hline(yintercept = 0.8)+
  #coord_cartesian(ylim = c(0,3))+
  labs(y = "hr/ watt / week")+
  theme_light()
```



### Summarise the metrics for each season

## Funkfunctions/aggregate_seasons.Rion Wochen Aggregation
```{r}
data_season <- generate_season_summary(lactat_calculated, data_gc, duration_weeks = 12)
```

```{r}
plot_w_duration <- function(plot_data, duration_weeks){
  
  plt_duration <- plot_data %>% 
    ggplot(aes(y=w_2mmol))+
    geom_jitter(aes(x=duration, color = year))+
    #geom_vline(xintercept = activities_today$TSS)+
    geom_line(aes(x=duration, group = year, color = year))+
    labs(title = str_c("duration last ", duration_weeks, " weeks"))+
    theme_light()
  
  plt_tss <- plot_data %>% 
    ggplot(aes(y=w_2mmol))+
    geom_jitter(aes(x=TSS, color = year))+
    #geom_vline(xintercept = activities_today$TSS)+
    geom_line(aes(x=TSS, group = year, color = year))+
    geom_smooth(aes(x=TSS))+
    labs(title = str_c("TSS last ", duration_weeks, " weeks"))+
    theme_light()
  
  p_result = plt_duration / plt_tss
  return(p_result)
  
}

plot_w_duration(data_season, 12)
```


```{r}


duration_weeks =12 
calc_and_plot(lactat_calculated, data_gc,duration_weeks = 12)
```

```{r}
calc_and_plot(lactat_calculated, data_gc, 10)
```


```{r}
calc_and_plot(lactat_calculated, data_gc, 11)
```

#### Ausgangspunkt Leistung von Season finden

```{r}
lactat_calculated%>% arrange(date) %>% mutate(days = (date-lag(date)-12*7)) %>% arrange(desc(date))
```


Ergänzen mit es darf nicht in der zukunft liegen

```{r}
lactat_dates <- lactat_calculated %>% select(date)
result <- c()

i_n=1

for (i in seq_along(lactat_dates$date)) {
  for (ii in seq_along(lactat_dates$date)) {
      result_ii = tibble(date = lactat_dates$date[ii]) %>%
        mutate(date_other = lactat_calculated$date[i],
          days = date - date_other)
    result[[i_n]] <- result_ii  
  i_n = i_n +1
  }
}

dates_crossed <- bind_rows(result) %>% filter(date != date_other)


result_diff <- c()
for (weeks in c(4:20)) {
mean_diff = dates_crossed %>% group_by(date) %>%
                      mutate(season_diff = abs(days-7*weeks),
                             season_diff = as.integer(season_diff),
                             best_diff = min(abs(season_diff)))  %>% #filter(date == "2020-05-05")
                      filter(season_diff == best_diff) %>% ungroup() %>%
  summarise(mean_diff = mean(season_diff)) %>% mutate(weeks = weeks)  
  
result_diff[[weeks]] <- mean_diff

}

bind_rows(result_diff) %>% ggplot(aes(x=weeks))+ geom_line(aes(y=mean_diff))
```



#####   ALTES ----------------------------------

```{r}
files <- tibble(files = list.files("Results/")) %>% filter(str_detect(files,"ml_data_2")) %>% 
                mutate(files = str_c("Results/",files)) %>% pull()
files


aggregate_raw_data <- function(data){
  data_aggregated <- data %>% group_by(date,device, workout_code, start_time) %>%
                                
                                    summarise(duration_sec = max(sec),
                                               watt = mean(watt),
                                              hr = mean(hr))
  
  return(data_aggregated)
}



data_aggregated_list <- list()
for (i in seq_along(files)) {
    data_raw<- read_rds(files[i])
    data_aggregated_list[[i]] <- data_raw %>% aggregate_raw_data()
    
  
}

data_aggregated <- bind_rows(data_aggregated_list)

data_aggregated
```


```{r}
activites_aggregated_list <- list()
for (i in seq_along(lactat_calculated$date)) {
  date_start = lactat_calculated$date_start[i]
  date_end = lactat_calculated$date[i]
  
  w_2mmol <- lactat_calculated$w_2mmol[i]
  w_5mmol <- lactat_calculated$w_5mmol[i]
  
  dates = tibble(date = seq(ymd(date_start), ymd(date_end), by = "1 day"))
  
  activities_data <- dates %>% left_join(data_aggregated) %>% filter(!is.na(workout_code))  
  
  activites_aggregated_list[[i]] <- activities_data %>% summarise(n = n(),
                                                       hr_time = sum(hr*duration_sec),
                                                       watt_time = sum(watt*duration_sec),
                                                       duration_sec_sum = sum(duration_sec)) %>%
                              mutate(duration = round(duration_sec_sum/3600,1),
                                     watt = watt_time / duration_sec_sum,
                                     hr = hr_time / duration_sec_sum,
                                     date_test = date_end,
                                     w_2mmol = w_2mmol,
                                     w_5mmol = w_5mmol)
  
}

activites_aggregated <- activites_aggregated_list %>% bind_rows()

activites_aggregated %>%
  ggplot(aes(x=date_test))+
  geom_line(aes(y = duration, color = "duration"))+
  geom_line(aes(y = w_2mmol, color = "2mmol"))+
  geom_line(aes(y = w_5mmol, color = "5mmol"))+
  geom_line(aes(y = hr, color = "hr"))+
  geom_line(aes(y = watt, color = "watt"))
```

```{r message=FALSE, warning=FALSE}

activites_aggregated %>%select(duration, w_2mmol, w_5mmol,watt, hr) %>% ggpairs()

```

```{r}
activites_aggregated %>%select(date_test, duration, w_2mmol, w_5mmol,n) %>% 
      filter(w_2mmol > 190 & duration <20)
```


### read trainings data
```{r}
data_2016_raw<- read_rds( "Results/test_ml_data_2016.rds")

data_2017_raw<- read_rds( "Results/test_ml_data_2017.rds")

data_2018_raw<- read_rds( "Results/test_ml_data_2018.rds")

data_2019_raw<- read_rds( "Results/test_ml_data_2019.rds")

data_2020_raw<- read_rds( "Results/test_ml_data_2020.rds")

data_2021_raw<- read_rds( "Results/test_ml_data_2021.rds")

data_2021_raw %>% summarise(max(date))
```

