---
title: "Create Season Data"
author: "ari"
date: "29 10 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Create Season data with the results from "Import_Data.Rmd" and a csv file called "Season_date_ftp.csv" which contains season name, end date of seson and the ftp at the end of the season.

The season should end with a ftp-test.

```{r}

library(tidyverse)
library(lubridate)
```

#Import data
```{r}

file_name_aggreagations <- "Results/aggregations_result_counts.rds"
file_name_watt_count <- "Results/watt_count_result.rds"
file_name_hr_count <- "Results/hr_count_result.rds"

path_laktat_ftp <- "C:/Users/rigle/Documents/Training/Laktat FTP/"

training_data_raw <- read_rds(str_c(path_laktat_ftp, file_name_aggreagations))
training_watt_count_raw <- read_rds(str_c(path_laktat_ftp, file_name_watt_count))
training_hr_count_raw <- read_rds(str_c(path_laktat_ftp, file_name_hr_count))

#=========================================================
#read the season date csv (season_name, end_date of season, end_ftp of season)

season_list <- read_csv2(str_c(path_laktat_ftp,"Season_date_ftp.csv"),
                         col_types = list("c","c","d")) %>%
                mutate(end_date=as.Date(end_date, "%d.%m.%Y"))
```

## Seasons

```{r}
season_list %>% ggplot(aes(x=end_date, y= end_ftp))+
  geom_point()
```



Calculate the sesaons and create  
season_date  
table.
```{r}
#================================Season functions==========================================
make_seasons <- function(d){
  #create a sequence of dates out of start date and end date
  season_date <- tibble(date = seq.Date(as.Date(d$start),
                                             as.Date(d$end_date), 
                                             by = "day") ) %>%
    mutate(season = d$season,
           end_ftp = d$end_ftp)
  return(season_date)
}

date_past <- function(date_sel, days_past = 150){ 
  #Calculate the date days_past days before the date date_sel
  daynr_past <- lubridate::yday(date_sel) -days_past
  year_past = year(date_sel)
  if(as.integer(daynr_past) < 0){
    year_past = year_past - 1
    daynr_past <- daynr_past +365
    date_past <- as.Date(strptime(paste(year_past, daynr_past), format="%Y %j"))
    
    return(date_past)
  }else{
        date_past <- as.Date(strptime(paste(year_past, daynr_past), format="%Y %j"))
    
    return(date_past)
  }
}





season_date_list <- list()
for(i in seq_along(season_list$season)){
  season <- season_list[i,]
  season$start <- date_past(date_sel = season$end_date, days_past = 150)
   season_date_list[[i]] <- make_seasons(season)
}

season_date <- bind_rows(season_date_list)
```



## Wrangle

### Clean
```{r}
training_data_clean<- training_data_raw %>% mutate(movement_time_sec = replace_na(movement_time_sec, 0),
                                                   TSS = replace_na(TSS,0),
                                                   IF = replace_na(IF,0)) 
```

### Add some information

```{r}
 training_data_clean<- training_data_clean %>% mutate(day = lubridate::yday(date)) 
```






## Create Season data
### Join with season data 

```{r}
training_data_season<- training_data_clean %>% right_join(season_date, by = "date")

training_watt_count_season<- training_watt_count_raw %>% right_join(season_date, by = "date")
training_hr_count_season<- training_hr_count_raw %>% right_join(season_date, by = "date")
```

### Clean
```{r}
training_data_season<- training_data_season %>% mutate(movement_time_sec = replace_na(movement_time_sec, 0),
                                                   TSS = replace_na(TSS,0),
                                                   IF = replace_na(IF,0)) 
```

```{r}


#Calculate the day_nr of the season:

calulate_day_nr <- function(d){

    d<- d %>% filter(!is.na(season)) %>%
      group_by(season) %>% arrange(date) %>% 
      mutate(day_season = rank(date, ties.method = "first"),
             day_season = as.numeric(date) - lag(as.numeric(date)),
             day_season = if_else(is.na(day_season),1,day_season),
             day_season = cumsum(day_season)) %>% ungroup()
    return(d)
}

training_data_season <- calulate_day_nr(training_data_season)

training_watt_count_season <- calulate_day_nr(training_watt_count_season)
training_hr_count_season <- calulate_day_nr(training_hr_count_season)
```



```{r}
training_data_season %>% group_by(season) %>% summarise(from = min(date),
                                               to = max(date),
                                               ftp = max(end_ftp),
                                               activities = n())
```

## Save
```{r}
training_data_season %>% write_rds(str_c(path_laktat_ftp,"Results/season_data_count.rds"))
training_watt_count_season %>% write_rds(str_c(path_laktat_ftp,"Results/season_watt_count.rds"))
training_hr_count_season %>% write_rds(str_c(path_laktat_ftp,"Results/season_hr_count.rds"))
```

