---
title: "Feature Pipeline"
author: "ari"
date: '2023-01-09'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description
Goal:
Create Features for a ML model, to predict the ftp based on the actual training data (history)

Input:
- ftp/laktat data (for the season dates and to calculate the right intensity and etc.)
  to use new laktat test use the file Analyse_season_v1.Rmd
- weeks/season
- gc activities aggregated/activity
- Interval aggregations

Output:
Aggregation of every season as a feature

## Parameters
```{r}
library(tidyverse)
library(patchwork)
library(lubridate)

source("functions_ftp_laktat.R")
source("functions_import.R")
source("functions_sesons.R")
source("functions_intervall.R")
```

```{r}
weeks_per_season = 12


intensity_min <- 0.88 #minimum intensity to count as an Interval intensity = watt_interval_mean/watt_ftp
device_list = c("BAsso_Vector", "P2M", "P2Cros", "P2MIndoor") # List of trust able devices for interval aggregation

path_ftp_tests <- "C:/Users/rigle/Documents/Training/Laktat FTP/laktat_watt_ftp.csv"
path_intervalls <- "Results/intervall_aggregation.csv"
path_activities <- "Results/goldencheetah_tss.csv"
path_activities_raw <- "C:/Users/rigle/AppData/Local/GoldenCheetah/Andl/activities/"   
```

## FTP / Laktat Data
```{r}

laktat_results<- read_csv2(path_ftp_tests) %>% mutate(date = as.Date(date, format = "%d.%m.%Y"))
```

### ftp values
```{r}
ftp_values <- add_missing_dates(laktat_results,colname="w_5mmol")

ftp_values%>% #arrange(desc(date))
  ggplot(aes(x=date, y = w_5mmol))+
  geom_line()+
  geom_vline(xintercept = as.Date(c("2016-01-01", "2016-04-15")), linetype = 2, color = "orange")+
  geom_vline(xintercept = as.Date(c("2017-03-01", "2017-04-15")), linetype = 2, color = "blue")+
  geom_vline(xintercept = as.Date(c("2023-01-01", "2023-04-15")), linetype = 2, color = "green")
```

```{r}
ftp_values %>% mutate(day = yday(date),
                      year = year(date)) %>%
  filter(day > 7 &
           day <= yday(Sys.Date())) %>%
  group_by(year) %>% arrange(day) %>% summarise(ftp_start = first(w_5mmol),
                                                ftp_end = last(w_5mmol)) %>%
  mutate(progress = ftp_end - ftp_start) %>% arrange(desc(progress)) %>%
  ggplot(aes(y = as.factor(year)))+
  geom_col(aes(x = progress, fill = ftp_start))+
  theme_light()
```

```{r}
plot_ftp_data <- ftp_values %>% mutate(day = yday(date),
                      year = year(date)) %>%
  group_by(year) %>%
  mutate(ftp_max_year = max(w_5mmol)) %>%
  filter(day > 7 &
           day <= yday(Sys.Date())) %>%
                     arrange(day) %>% summarise(ftp_start = first(w_5mmol),
                                                ftp_end = last(w_5mmol),
                                                ftp_max_year = max(ftp_max_year)) %>%
  mutate(progress = ftp_end - ftp_start,
         progress_type = case_when(progress > 0 ~ "positive", TRUE ~ "negative")) %>% arrange(desc(progress)) 

plot_ftp_data%>% mutate(progress_text = str_c(round(progress/ftp_start*100,1), " % ",round(progress), " W")) %>%
  

ggplot(aes(y = year))+
  
  geom_rect(aes(xmin = ftp_start, xmax = ftp_end, ymin = year-0.3, ymax = year+0.3,
                                            fill = progress_type))+
  geom_rect(aes(xmin = ftp_start, xmax = ftp_max_year, ymin = year-0.3, ymax = year+0.3),
            fill = "grey", alpha = 0.5)+
  geom_rect(aes(xmin = ftp_start, xmax = ftp_start+0.3, ymin = year-0.3, ymax = year+0.3),
                                            fill = "black")+
  geom_text(aes(x=ftp_start+(ftp_end-ftp_start)/2, y=year, label=progress_text), size=3.5)+
  
  #geom_rect(aes(xmin = 270, xmax = 290, ymin = 2019, ymax = 2019+0.6),
  #          fill = "grey", alpha = 0.3)+
  #geom_text(aes(x=280, y=2019.3, label="maximum FTP of this year"), size=3.5)+
  
  labs(title = "FTP progress till today per year",
       caption = "grey .. maximum FTP of this year",
       x = "FTP [W]",
       y="")+
  theme_light()+
  theme(legend.position = "")
  
  
  

```

### Calculate difference and progress

wie genau?
 - vom letzten ftp test an (auch wenn der 4 wochen vorher war)
 - Wert von 12 Wochen davor (der aktuelle Test, oder Wert des Verlaufes?)
 - verschiedene werte für verschiedene wochen
 - Verlauf und kein Progress- Progress berechnet sich dann aus den seasons (min und max)  --> probieren!


```{r}
#=========================== Laktat Curve =============================================

calculate_ftp_progress <- function(df){
  #adds the ftp progress
  library(zoo)
  
  df <- df %>% ungroup() %>% arrange(date) %>% mutate(FTP_progress = w_5mmol - lag(w_5mmol))
  
  
  #
  return(df)
}

calculate_ftp_progress(laktat_results) %>% select(date,w_5mmol, FTP_progress)
```


```{r}
add_missing_dates_2 <- function(df, colname){
  #adds the ftp progress
  library(zoo)
  
  df <- df %>% ungroup() %>% arrange(date) %>% mutate(FTP_progress = w_5mmol - lag(w_5mmol)) 
  
  # The progress is linked to the season before
  df <- df %>% mutate(FTP_progress_2 = lag(FTP_progress))
  
  #creates a tibble with all dates between the first test and today
  #with the last known value of the colname for each day
  
  dates <- tibble(date = seq(min(df$date), Sys.Date(), by = "day"))
  
  result <- dates  %>% left_join(df, by = "date") %>% select(date, colname,FTP_progress) %>% #zoo::na.locf()
                            
  mutate(FTP_progress2 = na.locf0(FTP_progress, fromLast = TRUE))%>%na.locf()
  
  return(result)
}

test <- add_missing_dates_2(laktat_results,colname="w_5mmol") 

test %>% filter(date > "2016-01-01" &
                date < "2018-01-01") %>%
  mutate(control = w_5mmol+FTP_progress2) %>%
  ggplot()+
  geom_point(aes(x=date, y = FTP_progress2))+
  geom_point( aes(x=date, y = w_5mmol, color = "test all"))+
  geom_point( aes(x=date, y = control , color = "test all + progress"))

  
```

#### only the absolut value

```{r}
laktat_results_progress <- calculate_ftp_progress(laktat_results) 
```


#### linear

```{r}
laktat_test_data <- tibble(date = as.Date(c("2023-01-07","2023-01-10", "2023-01-13")),
                           FTP = c(210,200,230))

calculate_ftp_progress_linear <- function(df){
  library(lubridate)
  library(zoo)
  
  df <- df %>% mutate(FTP_prev = lag(FTP),
                      Test = TRUE,
                      FTP_diff = FTP - FTP_prev,
                      days = as.integer(date - lag(date)),
                      FTP_per_day = FTP_diff/(days))
  
  dates <- tibble(date = seq(min(df$date), Sys.Date(), by = "day"),
                  day = yday(date))
  
  result <- dates  %>% left_join(df, by = "date") %>% 
                    mutate(date_test = case_when((date == Sys.Date()) |
                                                  (Test == TRUE) ~  date))
  
  result <- result %>% mutate(date_test = na.locf0(date_test, fromLast = TRUE),
                              FTP  = na.locf0(FTP, fromLast = TRUE),
                              FTP_prev  = na.locf0(FTP_prev, fromLast = TRUE),
                              FTP_per_day = na.locf0(FTP_per_day, fromLast = TRUE),
                              FTP_per_day = na.locf0(FTP_per_day, fromLast = TRUE))
  
   result <- result %>% group_by(date_test) %>% arrange(date) %>%
                            mutate(FTP_add = cumsum(FTP_per_day),
                                   FTP2 = case_when(Test == TRUE ~ FTP,
                                                   TRUE ~ FTP_prev+FTP_add)) %>%
     select(date,day, FTP, FTP2, FTP_per_day, everything())
  
  return(result)
}
```


```{r}
laktat_results_linear <- calculate_ftp_progress_linear(laktat_results %>% mutate(FTP = w_5mmol)) 

laktat_results_linear%>% #filter(date > "2017-11-29") %>% arrange(date) %>% select(date,day, FTP, FTP2)
  ggplot(aes(x = date))+
  geom_line(aes(y= FTP, color = "only values"))+
  geom_line(aes(y=FTP2, color = "interpolating"))+
  #geom_smooth(aes(y=FTP))+
  theme_light()

```

```{r}
weeks_test <- 8

laktat_results_linear %>% ungroup() %>% mutate(ftp_prev_linear = lag(FTP2,n = weeks_test*12)) %>% 
  filter(Test== TRUE& date > "2020-06-01") %>%
  ggplot(aes(x=date))+
  geom_point(aes(y=ftp_prev_linear, color = "prev linear"))+
  geom_line(aes(y=ftp_prev_linear, color = "prev linear"))+
  geom_point(aes(y=FTP_prev, color = "prev- value"))+
  geom_line(aes(y=FTP_prev, color = "prev- value"))+
  geom_line(aes(y=FTP, color = "FTP"))+
  theme_light()
```

```{r}
plot_data <- laktat_results_linear %>% ungroup() %>% 
  mutate(ftp_prev_linear = lag(FTP2,n = weeks_test*12),
         progress = FTP - FTP_prev,
         progress_linear = FTP - ftp_prev_linear) 

plot_data%>% 
  
  filter(Test== TRUE & date > "2022-06-01") %>%
  ggplot(aes(x= date))+
  geom_point(aes(y=progress_linear, color = "linear"))+
  geom_point(aes(y=progress, color = "prev- value"))+
  geom_line(aes(y=progress_linear, color = "linear"))+
  geom_line(aes(y=progress, color = "prev- value"))+
  theme_light()
```

#### proportional to TSS

```{r}
data_gc_test <-  read_csv(path_activities)

data_gc_test <- prepare_gc_summary(data_gc_test)
```

```{r}
data_gc_test %>% full_join(laktat_results, by="date") %>% 
  arrange(date) %>%
  mutate(test_nr =case_when(!is.na(w_5mmol) ~ 1, TRUE ~0),
         test_nr = cumsum(test_nr)) %>% 
  
  group_by(test_nr) %>% summarise(date_min = min(date),
                                  date_max = max(date),
                                  FTP = max(w_5mmol,na.rm = TRUE),
                                  TSS = sum(TSS,na.rm = TRUE))
  
```

if positive progress -> proportional to TSS (maybe days without TSS no progress)

if negative progress -> days without TSS are the worst 
thirst try: 
count all days, days with more than 30TSS - doesn't count.
days < 30TSS count(1/TSS), every day without TSS counts 1

```{r}
calculate_ftp_progress_tss2 <- function(df, df_gc_activities){
  library(lubridate)
  library(zoo)
  
  df <- df %>% mutate(FTP_prev = lag(FTP),
                      Test = TRUE,
                      FTP_diff = FTP - FTP_prev,
                      days = as.integer(date - lag(date)),
                      FTP_per_day = FTP_diff/(days))
  
  dates <- tibble(date = seq(min(df$date), Sys.Date(), by = "day"),
                  day = yday(date))
  
  result <- dates  %>% left_join(df, by = "date") %>% 
                    mutate(date_test = case_when((date == Sys.Date()) |
                                                  (Test == TRUE) ~  date))
  result <- result %>% left_join(df_gc_activities %>% select(date, TSS), by = "date")
  
  
  result <- result %>% mutate(date_test = na.locf0(date_test, fromLast = TRUE),
                              days = na.locf0(days, fromLast = TRUE),
                              FTP  = na.locf0(FTP, fromLast = TRUE),
                              FTP_prev  = na.locf0(FTP_prev, fromLast = TRUE),
                              progress = FTP - FTP_prev,
                              TSS = case_when(is.na(TSS)~0, TRUE~TSS), 
                              day_count = case_when((progress < 0) & (TSS == 0) ~1,
                                                    (progress < 0) & (TSS < 30) ~1/TSS,
                                                    TRUE ~0))
  
   result <- result %>% group_by(date_test) %>% arrange(date) %>%
                            mutate(TSS_sum = sum(TSS),
                                   FTP_TSS = (FTP - FTP_prev)/TSS_sum,
                                   FTP_add = FTP_TSS*TSS,
                                   FTP_add_neg = (FTP - FTP_prev)*day_count/days, 
                                   FTP_cumsum = case_when(progress >0 ~ cumsum(FTP_add),
                                                          TRUE ~ cumsum(FTP_add_neg)),
                                   FTP2 = case_when(Test == TRUE ~ FTP,
                                                   TRUE ~ FTP_prev+FTP_cumsum))# %>%
     #select(date,day, FTP, FTP2, FTP_per_day, FTP_cumsum,everything())
  
  return(result)
}

laktat_results_TSS2 <- calculate_ftp_progress_tss2(laktat_results %>% mutate(FTP = w_5mmol), data_gc_test) 

laktat_results_TSS2%>% filter(date > "2021-11-29"  & date < "2022-11-29") %>% 
  ggplot(aes(x = date))+
  geom_line(aes(y= FTP-250, color = "only values"))+
  geom_line(aes(y=FTP2-250, color = "interpolating"))+
  geom_col(aes(y=FTP_cumsum,), alpha = 1/3)+
  #geom_smooth(aes(y=FTP))+
  theme_light()

laktat_results_TSS2 %>% filter(progress <0)
```



```{r}
calculate_ftp_progress_tss <- function(df, df_gc_activities){
  library(lubridate)
  library(zoo)
  
  df <- df %>% mutate(FTP_prev = lag(FTP),
                      Test = TRUE,
                      FTP_diff = FTP - FTP_prev,
                      days = as.integer(date - lag(date)),
                      FTP_per_day = FTP_diff/(days))
  
  dates <- tibble(date = seq(min(df$date), Sys.Date(), by = "day"),
                  day = yday(date))
  
  result <- dates  %>% left_join(df, by = "date") %>% 
                    mutate(date_test = case_when((date == Sys.Date()) |
                                                  (Test == TRUE) ~  date))
  result <- result %>% left_join(df_gc_activities %>% select(date, TSS), by = "date")
  
  
  result <- result %>% mutate(date_test = na.locf0(date_test, fromLast = TRUE),
                              FTP  = na.locf0(FTP, fromLast = TRUE),
                              FTP_prev  = na.locf0(FTP_prev, fromLast = TRUE),
                              FTP_per_day = na.locf0(FTP_per_day, fromLast = TRUE),
                              FTP_per_day = na.locf0(FTP_per_day, fromLast = TRUE))
  
   result <- result %>% group_by(date_test) %>% arrange(date) %>%
                            mutate(TSS = case_when(is.na(TSS)~0, TRUE~TSS), 
                                   TSS_sum = sum(TSS),
                                   FTP_TSS = (FTP - FTP_prev)/TSS_sum,
                                   FTP_add = FTP_TSS*TSS,
                                   FTP_cumsum = cumsum(FTP_add),
                                   FTP2 = case_when(Test == TRUE ~ FTP,
                                                   TRUE ~ FTP_prev+FTP_cumsum)) %>%
     select(date,day, FTP, FTP2, FTP_per_day, FTP_cumsum,everything())
  
  return(result)
}


laktat_results_TSS <- calculate_ftp_progress_tss(laktat_results %>% mutate(FTP = w_5mmol), data_gc_test) 

laktat_results_TSS%>% #filter(date > "2017-11-29") %>% arrange(date) %>% select(date,day, FTP, FTP2)
  ggplot(aes(x = date))+
  geom_line(aes(y= FTP-250, color = "only values"))+
  geom_line(aes(y=FTP2-250, color = "interpolating"))+
  geom_col(aes(y=FTP_cumsum,), alpha = 1/3)+
  #geom_smooth(aes(y=FTP))+
  theme_light()
```


#### exponential


```{r}


laktat_test_data <- tibble(date = as.Date(c("2023-01-07","2023-01-10", "2023-01-13")),
                           FTP = c(210,200,230))

test_function <- function(df){
  library(lubridate)
  library(zoo)
  
  df <- df %>% mutate(FTP_prev = lag(FTP),
                      Test = TRUE,
                      FTP_diff = FTP - FTP_prev,
                      days = as.integer(date - lag(date)),
                      FTP_per_day = FTP_diff/(days))
  
  dates <- tibble(date = seq(min(df$date), Sys.Date(), by = "day"),
                  day = yday(date))
  
  result <- dates  %>% left_join(df, by = "date") %>% 
                    mutate(date_test = case_when((date == Sys.Date()) |
                                                  (Test == TRUE) ~  date))
  
  result <- result %>% mutate(date_test = na.locf0(date_test, fromLast = TRUE),
                              FTP  = na.locf0(FTP, fromLast = TRUE),
                              FTP_prev  = na.locf0(FTP_prev, fromLast = TRUE),
                              FTP_per_day = na.locf0(FTP_per_day, fromLast = TRUE),
                              FTP_per_day = na.locf0(FTP_per_day, fromLast = TRUE))
  
   result <- result %>% group_by(date_test) %>% arrange(date) %>%
                            mutate(FTP_add = cumsum(FTP_per_day),
                                   FTP2 = case_when(Test == TRUE ~ FTP,
                                                   TRUE ~ FTP_prev+FTP_add)) %>%
     select(date,day, FTP, FTP2, FTP_per_day, everything())
  
  return(result)
}

test_function(laktat_results %>% mutate(FTP = w_5mmol)) %>% #filter(date > "2017-11-29") %>% arrange(date) %>% select(date,day, FTP, FTP2)
  ggplot(aes(x = date))+
  geom_line(aes(y= FTP, color = "only values"))+
  geom_line(aes(y=FTP2, color = "interpolating"))+
  geom_smooth(aes(y=FTP))
```


exponential unten:
parameter passen noch nicht - gibts doch log rechenregeln um hochzahlen zu entschärfen?
```{r}
test <- tibble(x = seq(1,10,0.1))

final <- 4

quot <- 7

max(test$x) - log(final)/log(quot)

max(test$x) - final^(1/quot)

test %>% mutate(y_2 = 2^(x-8),
                y_3 = 7^(x-9.287586),
                #y_1_5 = 1.5^(x-9.287586),
                y_e = exp(1/x)) %>%
  ggplot()+
  geom_point(aes(y = y_2, x=x, color = "2"))+
  geom_point(aes(y = y_3, x=x, color = "3"))
  #geom_point(aes(y = y_1_5, x=x, color = "1.5"))
  #geom_point(aes(x = x, y=y_e, color = "exp"))
```


```{r}
exp_trend <-function(df,final_value, quote){
  coef = max(df$x) - log(final_value)/log(quote)
  coef_neg = log(final_value)/log(quote) + min(df$x)
  
  df <- df %>% mutate(y = final_value -quote^(coef_neg - x),
                      y_2 = quote^(coef_neg - x))
  
  return(df)
}

exp_trend(test, final_value = 6, quote = 1.7)%>%
  ggplot()+
  geom_point(aes(y = y, x=x))+
  geom_point(aes(y = y_2, x=x, color = "neg"))
```


```{r}
quotes_list <- c(1.3,1.5, 1.7)


results <- list()

for (i in seq_along(quotes_list)) {
  results[[i]] <- exp_trend(test, final_value = 6, quote = quotes_list[i]) %>%
    mutate(quote =  as.factor(quotes_list[i])) 
  
}

bind_rows(results)%>%
  ggplot()+
  #geom_point(aes(y = y, x=x, color = quote))#+
  geom_point(aes(y = y_2, x=x, color = quote))
```

```{r}
exp_trend <-function(df,final_value, quote){
  coef = max(df$x) - log(final_value)/log(quote)
  coef_neg = log(final_value)/log(quote) + min(df$x)
  
  df <- df %>% mutate(improvement = final_value -quote^(coef_neg - x),
                      decrease = quote^(coef_neg - x))
  
  return(df)
}
```

for loop jedes datum anwenden und in neuem df appenden (list function...)
x wird sind einfach die tage zwischen den datums

```{r}
laktat_test_data <- tibble(date = as.Date(c("2023-01-07","2023-01-10", 
                                            "2023-01-13", "2023-01-16",
                                            "2023-01-17", "2023-01-21")),
                           FTP = c(210,200,230,200,250,180))


FTP_exp <- function(df, quote_exp = 1.5){
  
    df <- df %>% mutate(date_test_before = lag(date),
                        FTP_test_before = lag(FTP))
    
    result_list <- list()
    for (i in c(2:4)) {
      
      laktat_test_date <- df[i,] 
      
      FTP_difference <- laktat_test_date$FTP - laktat_test_date$FTP_test_before
      
      dates_data <- tibble(date = seq(laktat_test_date$date_test_before,
                                      laktat_test_date$date, 
                                      by = "day"),
                           FTP = laktat_test_date$FTP) %>%
                                    mutate(x =row_number(),
                                           FTP_diff = FTP_difference) 
    
      dates_data <- exp_trend(dates_data, abs(FTP_difference), quote_exp)
      
      if (!is.na(FTP_difference)) {
        
     
        if (FTP_difference > 0  ) {
          result_list[[i]] <- dates_data %>% mutate(FTP2 = FTP - FTP_difference+ improvement)
          
        }else{
          result_list[[i]] <- dates_data %>%mutate(FTP2 = FTP  + decrease)
        }
      }
        

      
    }

    print(FTP_difference)
 return(bind_rows(result_list))
}

 
 FTP_exp(laktat_test_data) %>% 
   ggplot(aes(x=date)) +
   geom_line(aes(y=FTP))+
   geom_line(aes(y=FTP2, color = "exp"))#+
   geom_line(aes(y=FTP3, color = "exp 2"))
   
```

erste tag sollte am FTP test tag sein - ist das so?
letzte tag sollte der nächste ftp tag sein (dann ist die ftp erreicht) - oder ein tag davor,
weil die funktion den wert ansonsten nicht erreicht?
```{r}
FTP_exp(laktat_test_data)
```




### Calculate the FTP from the Lactat

Analyse_seasons_v1.Rmd

## Activity data

```{r}
data_gc <-  read_csv(path_activities)

data_gc <- prepare_gc_summary(data_gc)
```


## Intervals

### update intervals



```{r}
data_intervals_raw <- update_intervals(path_activities_raw, path_intervalls)
```








### process intervalls


```{r}
# get the real intervals based on the ftp value
source("functions_intervall.R")
data_intervals <- extract_intervals(data_intervals_raw, device_list, ftp_values)



plot_data_intervall_time <- data_intervals %>% mutate(year = lubridate::year(date),
                          year = as.factor(year)) %>% 
                      group_by(year) %>% arrange(date) %>% mutate(min = cumsum(min),
                                                                  min_sst = cumsum(min_sst),
                                                                  min_ftp = cumsum(min_ftp),
                                                                  min_vo2max = cumsum(min_vo2max),
                                                                  day = lubridate::yday(date))

behind_plan <- plot_data_intervall_time %>% 
                      filter(date == max(plot_data_intervall_time$date)) %>% 
                            summarise(min = max(min)) %>%
                            mutate(min_plan = lubridate::yday(Sys.Date())*60/5,
                                   min_diff = min_plan - min) %>% 
                            select(min_diff) %>% pull()

plot_data_intervall_time %>%
  filter(day < 200 & year %in% c(2016,2017,2018,2021, 2022,2023)) %>%
  ggplot(aes(x=day, y = min/60,color = year)) + 
  geom_line() +
  geom_point() +
  
  geom_point(aes(x=c(50),y = c(10), color = "2023"), size = 3)+
  geom_point(aes(x=c(84),y = c(16.8), color = "2023"), size = 3)+
  
  geom_vline(xintercept = lubridate::yday(Sys.Date()), linetype = 2)+
  geom_abline(slope = 0.2, linetype = 3)+
  
  
  # highest wattage after 2017:   (Is this true??)
  geom_vline(xintercept = lubridate::yday("2021-01-28"), linetype = 2,color = "red")+
  geom_abline(slope = (750/60)/(12*7), linetype = 2,color = "red")+
  labs(y = "hours",
       title = str_c("intervall time,   missing: ", behind_plan, " min"))+
  theme_light()

```

```{r}
plot_data_gc <- data_gc %>%  mutate(year = lubridate::year(date),
                          year = as.factor(year)) %>% 
                      group_by(year) %>% arrange(date) %>% mutate(duration = cumsum(duration),
                                                                  day = lubridate::yday(date)) %>%
                          ungroup()

if(max(plot_data_gc$date) != Sys.Date()){
  
  data_today <- plot_data_gc %>% filter(date == max(plot_data_gc$date)) %>% 
    mutate(date = Sys.Date())
  
  plot_data_gc <- plot_data_gc %>% bind_rows(data_today)
}

duration_today = plot_data_gc %>% filter(date == Sys.Date()) %>% select(duration) %>% pull()
duration_21 = plot_data_gc %>% filter(day == yday(Sys.Date()) &
                          year == 2021) %>% select(duration) %>% pull()

duration_missing = round(duration_21- duration_today,1)

plot_data_gc %>%
  filter(day < 200 & year %in% c(2016,2017,2020,2021, 2022,2023)) %>%
  ggplot(aes(x=day, y = duration,color = year)) + 
  geom_line() +
  geom_point() +
  geom_vline(xintercept = lubridate::yday(Sys.Date()), linetype = 2)+
  labs(y = "hours",
       title = str_c(duration_today, " h total duration , ", duration_missing, ' hours missing'))+
  theme_light()

```

```{r}
data_intervals %>% mutate(year= year(date)) %>% 
                  filter(intensity >1 & 
                          intensity <1.2 &
                            year %in% c(2016, 2017, 2020, 2021, 2022,2023)) %>% 
  
        select(date:hr, intensity, device,year) %>% 
  ggplot(aes(x = intensity, y = min))+
  geom_point(aes(color = as.factor(year)))+
  facet_wrap(year~.)
```

```{r}
data_intervals %>% mutate(year= year(date)) %>% 
                  filter(intensity >1.1 & 
                          intensity <1.2 &
                            year %in% c(2020) #& min > 20
                         ) %>% group_by(date, workout_code) %>% summarise(n=n(),
                                                                          watt = mean(watt))
  
     
```


## Join and aggregate


### progress

```{r}
generate_season_summary_progress <- function(lactat_data, data_gc, data_intervals_all, duration_weeks){
  # aggregates the activity data per season
  #
  # lactat_data ... tibble with date and watt_2mmol, watt_5mmol values for each season
  # data_gc ... activity data from gc 
  # data_intervals_all ... the intercal data
  # duration_weeks ... how many weeks are considered per season?
  #
  # the date of today is also included as a season
  
  #----------- create season dates
  library(lubridate)
  today_date = tibble(date = today())
  
  lactat_calculated <- lactat_data  %>% bind_rows(today_date) %>% 
    mutate(date_start = date - weeks(duration_weeks)) 
  
  #--------------
  activites_aggregated_list <- list()
  for (i in seq_along(lactat_calculated$date)) {
    date_start = lactat_calculated$date_start[i]
    date_end = lactat_calculated$date[i]
    
    watt_2mmol <- lactat_calculated$w_2mmol[i]
    watt_5mmol <- lactat_calculated$w_5mmol[i]
    ftp_progress <- lactat_calculated$FTP_progress[i]
    
    #---------- create dates of season for filtering
    dates = tibble(date = seq(ymd(date_start), ymd(date_end), by = "1 day"))
    
    date_char <- function(df){
      #joining with characters is safer
      df %>% mutate(date = as.character(date))
    }
    
    activities_data <- date_char(dates) %>% left_join(date_char(data_gc), by = "date") %>%
      filter(duration > 0) %>%
      mutate(date = as.Date(date))
    
    data_intervals <-  date_char(dates) %>% 
      left_join(date_char(data_intervals_all), by = "date") %>% filter(!is.na(watt)) %>% 
      mutate(date = as.Date(date))
    
    #---------------  aggregation -------------
    aggregation_1 <- activities_data %>% 
      mutate(long = case_when(duration >= 3 ~ 1, TRUE ~ 0),
             high_TSS = case_when(TSS > 100 ~1, TRUE ~ 0)) %>%
      
      summarise(n = n(),
                n_long = sum(long, na.rm = TRUE),
                n_high_TSS = sum(high_TSS, na.rm = TRUE),
                TSS = sum(TSS, na.rm = TRUE),
                duration = sum(duration, na.rm = TRUE)) %>%
      mutate(date_test = date_end,
             watt_2mmol = !!watt_2mmol,
             watt_5mmol = !!watt_5mmol,
             ftp_progress = !!ftp_progress)
    
    aggregation_watt <- activities_data %>% filter(w_mean>0) %>%
      summarise(n_bike = n(),
                watt = mean(w_mean, na.rm = TRUE))
    aggregation_intervals <- data_intervals %>% #filter(intensity > intensity_min) %>%
      summarise(n_interval = n(),
                interval_watt = mean(watt, na.rm = TRUE),
                interval_hr = mean(hr, na.rm = TRUE),
                interval_min = sum(min, na.rm = TRUE))
    
    activites_aggregated_list[[i]]  <- aggregation_1 %>% bind_cols(aggregation_watt) %>% bind_cols(aggregation_intervals)
  }
  
  result= bind_rows(activites_aggregated_list) %>% 
    distinct(date_test, .keep_all = TRUE) %>%
    mutate(year = lubridate::year(date_test) %>% as.factor())
  
  return(result)
}
```


```{r}
weeks_per_season=12

data_season_progress <- generate_season_summary_progress(lactat_data = laktat_results_progress, 
                                  data_gc = data_gc, 
                                  data_intervals = data_intervals,
                                  weeks_per_season)

data_season_progress <- data_season_progress %>% mutate(month = month(date_test))
```

```{r}
last_test_date <- data_season_progress %>% filter(!is.na(ftp_progress)) %>% summarise(date_test = max(date_test))
last_test <- data_season_progress %>% filter(date_test == last_test_date)

data_season_progress %>% 
  ggplot(aes(x = interval_min ))+
  geom_point(aes(y = ftp_progress, color =year))+
  geom_point(data = last_test,aes(y = ftp_progress, color =year), size = 4)+
  facet_wrap(month~.)+
  geom_hline(yintercept = 0)+
  theme_light()

data_season_progress %>% 
  ggplot(aes(x = duration ))+
  geom_point(aes(y = ftp_progress, color =year))+
  geom_point(data = last_test,aes(y = ftp_progress, color =year), size = 4)+
  geom_hline(yintercept = 0)+
  theme_light()
```

```{r}
data_plot <- data_season_progress %>% filter(year %in% c(2016,2017,2018,2020,2021,2022,2023)) %>%
                          group_by(year) %>% arrange(date_test) %>% 
                                mutate(progress_year = cumsum(ftp_progress) - first(ftp_progress)) 

p_progress <- data_plot %>%
  
  ggplot(aes(x =yday(date_test) ))+
  geom_line(aes(y = progress_year, color =as.factor(year)))+
  geom_point(aes(y = progress_year, color =as.factor(year)))+
  geom_hline(yintercept = 0)+
  labs(title = "ftp progress since last test",
       color = "",
       x = "day")+
  theme_light()

p_ftp <- data_plot %>%
  
  ggplot(aes(x =yday(date_test) ))+
  geom_line(aes(y = watt_5mmol, color =as.factor(year)))+
  geom_line(data = data_plot %>% filter(year == 2023),
            aes(y = watt_5mmol, color =as.factor(year)),size =1)+
  geom_point(aes(y = watt_5mmol, color =as.factor(year)))+
  geom_hline(yintercept = 265, linetype = 3)+
  geom_vline(xintercept = yday("2023-08-27"), linetype = 3)+
  labs(title = "ftp test",
       color = "",
       x = "day")+
  theme_light()

p_ftp / p_progress
```

```{r}
data_season_progress %>% mutate(ftp_past = watt_5mmol - ftp_progress,
                                period = case_when(month < 2 ~ "start",
                                                   month < 4 ~ "build_up",
                                                   month < 8 ~ "peak",
                                                   TRUE~ "end")) %>%
  ggplot(aes(x= ftp_past))+
  geom_point(aes(y=ftp_progress,color = year))+
  geom_histogram(aes(x = watt_5mmol), binwidth = 5, alpha = 1/3)+
  geom_hline(yintercept = 0)+
  facet_wrap(period ~.)+
  labs(title = "ftp progress depending on the past ftp")+
  theme_light()
```

```{r}
data_season_progress %>% mutate(ftp_past = watt_5mmol - ftp_progress,
                                period = case_when(month < 2 ~ "start",
                                                   month < 4 ~ "build_up",
                                                   month < 8 ~ "peak",
                                                   TRUE~ "end")) %>%
  ggplot(aes(x= watt_5mmol))+
  geom_histogram(aes(x = watt_5mmol, fill = year), binwidth = 1)+
  geom_hline(yintercept = 0)+
  facet_wrap(period ~., ncol = 1, scales = "free_y")+
  theme_light()
```


4 Wochen passt nicht 2021-01-28 interval_watt 249W !! 100 min für 4 wochen
was habe ich davor gemacht ?? der test am 1.4. war auch super ???
die monate davor konsequent sst und ga1

```{r}
data_season_progress %>% filter(ftp_progress >= last_test$ftp_progress) %>%
  select(date_test, watt_2mmol:ftp_progress, TSS, n_high_TSS, duration, interval_watt,interval_min, everything())
```


### only ftp
```{r}
seasons_laktat_watt <- laktat_results 

data_season <- generate_season_summary(lactat_data = laktat_results, 
                                  data_gc = data_gc, 
                                  data_intervals = data_intervals,
                                  weeks_per_season)

#data_season %>% arrange(date_test) %>% select(year, date_test, everything())
```


```{r}
interval_month <- data_intervals %>% mutate(month = month(date),
                                            year = year(date)) %>% 
                        group_by(year, month) %>%
                              summarise(date = mean(date),
                                        interval_min = sum(min))

data_season  %>% #select(date_test, watt_5mmol, n_interval:interval_min) %>% 
  ggplot(aes(x=date_test)) + 
 # geom_point(aes(y= interval_min, color = watt_5mmol))+
  #geom_line(aes(y= interval_min, color = watt_5mmol))+
  geom_line(aes(y= watt_5mmol, color = "FTP"))+
  geom_line(aes(y= duration, color = "duration [h] in season"))+
  geom_col(data = interval_month, aes(x=date, y = interval_min), width = 30, alpha = 1/3)+
  geom_hline(yintercept = 260, linetype = 2)+
  labs(x = "",
       y = "",
       title = str_c(weeks_per_season, " weeks per season"),
       subtitle = "bars .. interval min per month")+
  theme_light()
```




```{r}

season_weeks <- c(4,6,8,10,12,16,18,20,22)

data_seasons_list <- list()

for (i in seq_along(season_weeks)) {
  
  weeks_sel <- season_weeks[i]
  
  data_seasons_list[[i]] <- generate_season_summary(lactat_data = laktat_results, 
                                  data_gc = data_gc, 
                                  data_intervals = data_intervals,
                                   weeks_sel)  %>% mutate(weeks = weeks_sel)
  
}

data_seasons <-  bind_rows(data_seasons_list) 

data_season_today <- data_seasons %>% filter(date_test == max(date_test))

years_sel <- c(2016,2017,2021,2022,2023)

data_seasons %>%  #
  mutate(year_plot = case_when(year %in% c(years_sel) ~ as.factor(year),
                               TRUE ~ as.factor("other"))) %>%
  ggplot(aes(x=interval_min)) + 
  geom_point(aes(y= watt_5mmol, color = year_plot))+
  geom_vline(data = data_season_today,aes(xintercept = data_season_today$interval_min), linetype = 2)+
  #scale_x_log10()+
  facet_wrap(weeks~., scales = "free_x")+
  theme_light()


```


```{r}
data_seasons %>%  #
  mutate(year_plot = case_when(year %in% c(years_sel) ~ as.factor(year),
                               TRUE ~ as.factor("other"))) %>%
  ggplot(aes(x=duration)) + 
  geom_point(aes(y= watt_5mmol, color = year_plot))+
  geom_vline(data = data_season_today,aes(xintercept = data_season_today$duration), linetype = 2)+
  #scale_x_log10()+
  facet_wrap(weeks~., scales = "free_x")+
  theme_light()
```



##### Einschub ML
Model für jede Kurve trainieren und FTP predicten

```{r}
test_data <- data_seasons %>%  filter(weeks == 12 &
                                        interval_min >0) %>% 
                  mutate(interval_min_2 = interval_min*interval_min,
                         interval_min_3 = interval_min*interval_min *interval_min,
                         interval_min_log = log10(interval_min))

 test_data  %>%
  mutate(year_plot = case_when(year %in% c(years_sel) ~ as.factor(year),
                               TRUE ~ as.factor("other"))) %>%
  ggplot(aes(x=interval_min)) + 
  geom_point(aes(y= watt_5mmol, color = year_plot))+
  geom_vline(data = data_season_today %>%  filter(weeks == 12),
             aes(xintercept = interval_min), linetype = 2)+
  theme_light()
```

```{r}
library(tidymodels)

set.seed(4595)
data_split <- initial_split(test_data,  prop = 0.75)

weeks_train <- training(data_split)
weeks_test  <- testing(data_split)
```

```{r}
lm_model <- linear_reg() %>% set_engine("lm")
```

```{r}
simple_weeks <- 
  recipe(watt_5mmol ~ interval_min + interval_min_2 + interval_min_log,
         data = weeks_train) 
```

```{r}
lm_wflow <- 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(simple_weeks)
 
lm_fit <- fit(lm_wflow, weeks_train)
```

```{r}
minutes <- tibble(interval_min = c(0:1500)) %>% 
                  mutate(interval_min_2 = interval_min*interval_min,
                         interval_min_3 = interval_min*interval_min *interval_min,
                         interval_min_log = log10(interval_min))

ml_result <- minutes %>% bind_cols(predict(lm_fit, minutes)) %>% rename(watt_5mmol_pred = .pred)

 test_data  %>%
  mutate(year_plot = case_when(year %in% c(years_sel) ~ as.factor(year),
                               TRUE ~ as.factor("other"))) %>%
  ggplot(aes(x=interval_min)) + 
  geom_point(aes(y= watt_5mmol, color = year_plot))+
   geom_line(data= ml_result, aes(x= interval_min, y = watt_5mmol_pred))+
  geom_vline(data = data_season_today %>%  filter(weeks == 12),
             aes(xintercept = interval_min), linetype = 2)+
  theme_light()
```


##### Einschub Ende

```{r}

data_seasons %>%  #select(date_test, watt_5mmol, n_interval:interval_min) %>% 
  ggplot(aes(x=interval_min)) + 
  geom_point(aes(y= watt_5mmol, color = as.factor(year)))+
  geom_vline(data = data_season_today,aes(xintercept = data_season_today$interval_min), linetype = 2)+
  scale_x_log10()+
  facet_wrap(weeks~., scales = "free_x")+
  theme_light()
```
```{r}
w_sel = 12

data_today <- data_seasons %>% filter(weeks == w_sel & date_test == Sys.Date()-1)
data_seasons %>% filter(weeks == w_sel) %>% 
  ggplot(aes(x=duration))+
  geom_jitter(aes(y=interval_min, color = year, size = watt_5mmol), alpha = 1)+
  geom_vline(xintercept = data_today$duration, linetype = 3)+
  geom_hline(yintercept = data_today$interval_min, linetype = 3)+
  #scale_x_log10()+
  theme_light()
```

```{r}
data_today <- data_seasons %>% filter(weeks == w_sel & date_test == Sys.Date())
```


```{r}
data_better_as_today <- data_seasons %>% filter(weeks == w_sel &
                        (duration >= data_today$duration &
                        interval_min >= data_today$interval_min)) %>% 
      arrange(watt_5mmol) %>% mutate(date = as.factor(date_test)) %>%
  select(date_test, watt_5mmol, duration, interval_min, everything()) 

#p_duration <- 
  data_better_as_today%>%
  ggplot(aes(x =duration))+
  geom_col(aes(y=watt_5mmol, fill = date))+
    geom_vline(xintercept = data_today$duration)+
    coord_cartesian(ylim = c(230,300))+
    theme_light()
  
  data_better_as_today%>%
  ggplot(aes(x =interval_min))+
  geom_col(aes(y=watt_5mmol, fill = date))+
    geom_vline(xintercept = data_today$interval_min)+
    coord_cartesian(ylim = c(230,300))+
    theme_light()
```


### Features

#### Model 1
Build a simple model with the features duration for different seasons to predict the FTP
How accurate is the model [W] RMSE. Feature Importance!
Null model: mean(FTP) or median(FTP)

```{r}
data_seasons  %>% summarise(FTP_mean = mean(watt_5mmol, na.rm = TRUE),
                                               FTP_median = median(watt_5mmol, na.rm = TRUE))
```


```{r}
data_seasons %>%  #select(date_test, watt_5mmol, n_interval:interval_min) %>% 
  ggplot(aes(x=duration)) + 
  geom_point(aes(y= watt_5mmol, color = as.factor(year)))+
  geom_vline(data = data_season_today,aes(xintercept = data_season_today$duration), linetype = 2)+
  scale_x_log10()+
  facet_wrap(weeks~., scales = "free_x")+
  theme_light()
```

```{r}
data_seasons_wider <- data_seasons %>% select(date_test, watt_5mmol, duration, weeks) %>%
                                        rename(FTP = watt_5mmol) %>%
                pivot_wider(values_from = duration, 
                            names_from = weeks,
                            names_glue = "week_{weeks}_dur")


#data_seasons_wider %>% write_csv2("Results/ml/ml_1/duration_ftp_seasons_wider.csv")
data_seasons_wider
```

#### Model 2
include interval minutes

```{r}
data_seasons %>%  #select(date_test, watt_5mmol, n_interval:interval_min) %>% 
        mutate(interval_min = log10(interval_min)) %>%
  ggplot(aes(x=interval_min)) + 
  geom_point(aes(y= watt_5mmol, color = as.factor(year)))+
  #geom_vline(data = data_season_today,aes(xintercept = data_season_today$interval_min), linetype = 2)+
  #scale_x_log10()+
  facet_wrap(weeks~., scales = "free_x")+
  theme_light()

```


```{r}
data_seasons_min_wider <- data_seasons %>% select(date_test, watt_5mmol, interval_min, weeks) %>%
                                        rename(FTP = watt_5mmol) %>%
                pivot_wider(values_from = interval_min, 
                            names_from = weeks,
                            names_glue = "week_{weeks}_dur")


#data_seasons_min_wider %>% write_csv2("Results/ml/ml_1/duration_ftp_seasons_min_wider.csv")
data_seasons_min_wider
```

The same but with log10 transformation
```{r}
data_seasons_min10_wider <- data_seasons %>% select(date_test, watt_5mmol, interval_min, weeks) %>%
                                        rename(FTP = watt_5mmol) %>%
                            mutate(interval_min = log10(interval_min)) %>%
                pivot_wider(values_from = interval_min, 
                            names_from = weeks,
                            names_glue = "week_{weeks}_dur")


data_seasons_min10_wider %>% write_csv2("Results/ml/ml_1/duration_ftp_seasons_min10_wider.csv")
```

