---
title: "Training_plots"
author: "ari"
date: "25 10 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

# Ideas
- ftp seperate into indoor and outdoor
- percentage of time in zines
- estimate w_2mmol for time before laktat measurement
- categorize activities
- detect a pattern
- define seasons

```{r}
path_laktat_ftp <- "C:/Users/rigle/Documents/Training/Laktat FTP/"

training_data_raw <- read_rds(str_c(path_laktat_ftp,"Results/aggregations_result.rds"))
```

## Seasons

Define the saeasons, Name and end date:
```{r}
season_list <-   tibble(season = c("2016","2017","2019","2021_Feb","2021_Apr","2021_Okt"), 
                      end = as.Date(c("2016-07-20","2017-05-22","2019-06-05","2021-02-26", "2021-04-21","2021-10-11")))
```

Calculate the sesaons and create  
season_date  
table.
```{r}
#================================Season functions==========================================
make_seasons <- function(d){
  #create a sequence of dates out of start date and end date
  season_date <- tibble(date = seq.Date(as.Date(d$start),
                                             as.Date(d$end), 
                                             by = "day") ) %>%
    mutate(season = d$season)
  return(season_date)
}

date_past <- function(date_sel, days_past = 150){ 
  #Calculate the date days_past days before the date date_sel
  daynr_past <- lubridate::yday(date_sel) -days_past
  year_past = year(date_sel)
  if(as.integer(daynr_past) < 0){
    year_past = year_past - 1
    daynr_past <- daynr_past +365
    date_past <- as.Date(strptime(paste(year_past, daynr_past), format="%Y %j"))
    
    return(date_past)
  }else{
        date_past <- as.Date(strptime(paste(year_past, daynr_past), format="%Y %j"))
    
    return(date_past)
  }
}





season_date_list <- list()
for(i in seq_along(season_list$season)){
  season <- season_list[i,]
  season$start <- date_past(date_sel = season$end, days_past = 150)
   season_date_list[[i]] <- make_seasons(season)
}

season_date <- bind_rows(season_date_list)


```



## Wrangle

### Clean
```{r}
training_data_clean<- training_data_raw %>% mutate(movement_time_sec = replace_na(movement_time_sec, 0),
                                                   TSS = replace_na(TSS,0),
                                                   IF = replace_na(IF,0)) 
```

### Add some information

```{r}
 training_data_clean<- training_data_clean %>% mutate(day = lubridate::yday(date)) 
```

## Create Season data
### Join with season data 

```{r}
training_data_season<- training_data_clean %>% right_join(season_date, by = "date")
```

### Clean
```{r}
training_data_season<- training_data_season %>% mutate(movement_time_sec = replace_na(movement_time_sec, 0),
                                                   TSS = replace_na(TSS,0),
                                                   IF = replace_na(IF,0)) 
```

```{r}


#Calculate the day_nr of the season:

training_data_season<- training_data_season %>% filter(!is.na(season)) %>%
  group_by(season) %>% arrange(date) %>% 
  mutate(day_season = rank(date, ties.method = "first"),
         day_season = as.numeric(date) - lag(as.numeric(date)),
         day_season = if_else(is.na(day_season),1,day_season),
         day_season = cumsum(day_season)) %>% ungroup()
```

# Analyze
```{r}
training_data_season %>% filter(!is.na(season)) %>% 
  ggplot(aes(x= day_season)) +
  geom_line(aes(y= ftp, color = "FTP"), size =1.3) +
  geom_line(aes(y= w_2mmol, color = "2 mmol"))+
  geom_line(aes(y= w_4mmol, color = "4 mmol"))+
  geom_line(aes(y= w_5mmol, color = "5 mmol")) +
  facet_wrap(season~.)
```



```{r}
training_data_season %>% filter(!is.na(season)) %>% 
  group_by(season) %>% arrange(day_season) %>%
   mutate(time_cum = cumsum(movement_time_sec)/(3600),
          TSS_cum = cumsum(TSS),
          IF_cum = cumsum(IF*movement_time_sec)) %>% 
  mutate(ftp = last(ftp)) %>%
  ungroup() %>%
   mutate(time_cum_rel = time_cum / max(time_cum)*100,
          TSS_cum_rel = TSS_cum / max(TSS_cum)*100,
          IF_cum_rel = IF_cum / max(IF_cum)*100) %>%
  
  
          pivot_longer(cols = c("TSS_cum", "time_cum", "time_cum_rel","TSS_cum_rel", "IF_cum_rel", "watt_mean", "hr_mean"), 
                       names_to = "metric")  %>%
  
  
  filter(metric %in% c("time_cum_rel","TSS_cum_rel", "IF_cum_rel", "watt_mean", "hr_mean")) %>%

  ggplot(aes(x= day_season)) +
  geom_line(aes(y = value, color = as.factor(ftp)))+
  facet_wrap(metric~., scales= "free")+
  labs(y = "Percent",
       x= "day of year")+
  theme_light()
```


```{r}
training_data_season %>% filter(!is.na(season)) %>% 
  group_by(season) %>% arrange(date) %>%
   mutate(time_cum = cumsum(movement_time_sec)/(3600),
          TSS_cum = cumsum(TSS),
          IF_cum = cumsum(IF*movement_time_sec)) %>% 
  ungroup() %>%
   mutate(time_cum_rel = time_cum / max(time_cum)*100,
          TSS_cum_rel = TSS_cum / max(TSS_cum)*100,
          IF_cum_rel = IF_cum / max(IF_cum)*100) %>%
  
  
          pivot_longer(cols = c("TSS_cum", "time_cum", "time_cum_rel","TSS_cum_rel", "IF_cum_rel", "watt_mean", "hr_mean"), 
                       names_to = "metric")  %>%
  
  
  filter(metric %in% c("watt_mean", "hr_mean")) %>%

  ggplot(aes(x= day_season)) +
  geom_line(aes(y = value, color = season))+
  geom_smooth(aes(y=value, color = season))+
  facet_wrap(metric~., scales= "free")+
  labs(y = "Percent",
       x= "day of year")+
  theme_light()
```
 
```{r}
training_data_clean %>% ggplot()+geom_histogram(aes(IF))
```


```{r}
training_data_season %>% filter(!is.na(season)) %>% 
  group_by(season) %>% arrange(day_season) %>%
   mutate(time_cum = cumsum(movement_time_sec)/(3600),
          TSS_cum = cumsum(TSS),
          IF_cum = cumsum(IF*movement_time_sec)) %>% 
  ungroup() %>%
   mutate(time_cum_rel = time_cum / max(time_cum)*100,
          TSS_cum_rel = TSS_cum / max(TSS_cum)*100,
          IF_cum_rel = IF_cum / max(IF_cum)*100) %>%
  mutate(IF_kat = case_when(IF > 0.8 ~ "high",
                            TRUE ~ " low")) %>%
  


  ggplot(aes(x= day_season)) +
  geom_point(aes(y = watt_mean, color = "watt_mean", size = IF_kat), alpha = 0.5)+
  geom_smooth(aes(y=watt_mean, color = "watt_mean"))+
    geom_point(aes(y = hr_mean, color = "hr_mean"))+
  geom_smooth(aes(y=hr_mean, color = "hr_mean"))+
  geom_hline(yintercept = 130)+
  facet_wrap(season~., scales= "free")+
  labs(y = "Percent",
       x= "day of year")+
  theme_light()
```



```{r}
training_data_clean %>% filter((date) > as.Date("2021-01-01")) %>% ggplot(aes(x= date)) +
  geom_line(aes(y= ftp, color = "FTP"), size =1.3) +
  geom_line(aes(y= w_2mmol, color = "2 mmol"))+
  geom_line(aes(y= w_4mmol, color = "4 mmol"))+
  geom_line(aes(y= w_5mmol, color = "5 mmol"))
```

`


```{r}
training_data %>% colnames()

training_data %>% ggplot(aes(x= date)) +
  geom_line(aes(y= movement_time_sec, color = "movement_time_sec"), size =1.3) +
  geom_line(aes(y= time_2mmol, color = "time_2mmol"))+
  geom_line(aes(y= time_4mmol, color = "time_4mmol"))+
  geom_line(aes(y= time_below_w_min, color = "time_below_w_min"))
```

```{r}
training_data %>% colnames()

training_data %>% ggplot(aes(x= date)) +
  geom_rug(aes(y= km, fill = "km")) +
  geom_point(aes(y= km, color = "km"))
```

